### 2019-12-14 Statistical Methods/04_probability.rmd
statistical method, ch 4
statistical method, ch 4

If X has a standard normal distribution with, determine:

@@

@@

@@

@@

@@

a.) $P(x \le 40)$

@@

@@

@@

@@

a.) $P(x < 22)$

@@

@@

@@

@@

@@

@@

@@

@@

Assuming that the scores on a math achievement test are normally distributed with $\mu = 69$ and standard deviation $\sigma = 10$, what is the probability of getting a score greater than 78?

@@

@@

Determien the probability that a randomly selected battery will last at least 62 months.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

If Z has a standard normal distribution with, determine:

@@

```{r, echo = T}
qnorm(0.0764, lower.tail = F)
```

@@

```{r, echo = T}
qnorm(0.504, lower.tail = F)
```

@@

```{r, echo = T}
qnorm((1 + 0.9108)/2)
```

@@

```{r, echo = T}
qnorm((1+.8)/2)
```

@@

a.) $P(X \le 40)$

```{r, echo = T}
pnorm(40, mean = 50, sd = 9)
```

@@

```{r, echo = T}
1 - pnorm(55, mean = 50, sd = 9, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(60, mean = 50, sd = 9, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(60, mean = 50, sd = 9) - pnorm(40, mean = 50, sd = 9)
```

@@

a.) $P(X < 22)$

```{r, echo = T}
1 - pnorm(22, mean = 20, sd = 9, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(17, mean = 20, sd = 9, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(15, mean = 20, sd = 9, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(38, mean = 20, sd = 5) - pnorm(2, mean = 20, sd = 9)
```

@@

```{r, echo = T}
pnorm(1, mean = .75, sd = .5) - pnorm(.5, mean = .75, sd = .5)
```

@@

```{r, echo = T}
pnorm(1.25, mean = .75, sd = .5) - pnorm(.25, mean = .75, sd = .5)
```

@@

```{r, echo = T}
qnorm((1 +.95)/2)
```

@@

```{r, echo = T}
qnorm((1 +.8)/2)
```

@@

Assuming that the scores on a math achievement test are normally distributed with $\mu = 68$ and standard deviation $\sigma = 10$, what is the probability of getting a score greater than 78?

```{r, echo = T}
pnorm(78, mean = 68, sd = 10, lower.tail = F)
```

@@

```{r, echo = T}
qnorm(1 - 0.05, mean = 68, sd = 10)
```

@@

Determine the probability that a randomly selected battery will last at least 62 months.

```{r, echo = T}
pnorm(62, mean = 58, sd = 3, lower.tail = F) # more than 62
```

@@

```{r, echo = T}
pnorm(1.15, mean = 1, sd = .1) - pnorm(.85, mean = 1, sd = .1)
```

@@

```{r, echo = T}
pnorm(0, mean = -300, sd = 100, lower.tail = F)
```

@@

```{r, echo = T}
pnorm(6, mean = 5, sd = 1) - pnorm(4, mean = 5, sd = 1)
```

@@

Suppose the daily amount of solar radiation in Los Angeles is normally distributed with mean 450 and sd 50.

Determine the probability that for a given day the radiation is between 350 and 550.

```{r, echo = T}
pnorm(5.5, mean = 4.5, sd = .5) - pnorm(3.5, mean = 4.5, sd = .5)
```

@@

If the cholesterol levels of adults are normally distributed with mean 230 and standard deviation 25, what is the probability that a randomly sampled adult has a cholesterol level greater than 260?

```{r, echo = T}
pnorm(2.6, mean = 2.3, sd = .25, lower.tail = F)
```

@@

If after 1 year, the annual mileage of privately owned cars is normally distributed with mean 14,000 miles and sd 3,500, what is the probability a car has greater than 20,000 miles?

```{r, echo = T}
pnorm(20, mean = 14, sd = 3.5, lower.tail = F)
```

@@

Can small changes in the tails of a distribution result in large changes in the population mean, $\mu$, relative to the changes in median?

_Yes, the mean is heavly influenced by the tails, where as the median is not._

@@

Explain in what sense the population variance is sensitive to small changes in a distribution.

_The variance is sensetive to small changes in the tail._

@@

For normal random variables, the probability of being within one standard deviation of the mean is .68. That is, $P(\mu - \sigma \le X \le \mu + \sigma) = .68$, if X has a normal distribution.

For nonnormal distribution, is it safe to assume that this probability is again .68?

_No. The AUC (and therefore the mean/variance relationship) for a distribution is defined by its pdf, $P(X) = F_x$, which will be unique per distribution._

@@

If a distribution appears to be bell-shaped and symmetric about its mean, can we assume that the probability of being within one sd of the mean is .68?

_No._

@@

Can two distribution differ by a large amount yet have equal means and variances?

@@

If a distribution is skewed, is it possible that the mean exceedes the .85 quantile?
